Cleaning Tropical Andes plant GBIF occurrence records

### 2024-03-07 code/L1/L1_P1_TropicalAndes_plants_GBIF.Rmd
Add data summary function

# Set file paths
```{r}
data_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

@@

```{r}
print("The number of records is")
nrow(TropicalAndes_GBIF_plant_occ_cleaned)
print("The number of species is")
length(unique(TropicalAndes_GBIF_plant_occ_cleaned$species))
print("The number of genera is" )
length(unique(TropicalAndes_GBIF_plant_occ_cleaned$genus))
print("The number of families is")
length(unique(TropicalAndes_GBIF_plant_occ_cleaned$family))
```

>>>>

# Set file paths
```{r}
data_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
source("~/GitHub/neotropical_plants/functions/data_summary.R")
```

@@

```{r}
data_summary(TropicalAndes_GBIF_plant_occ_cleaned, TropicalAndes_GBIF_plant_occ_cleaned$species, TropicalAndes_GBIF_plant_occ_cleaned$genus, TropicalAndes_GBIF_plant_occ_cleaned$family)
```
